Hypercoercions and a Framework for Equivalence of Cast Calculi

### 2019-10-22 paper.tex
progress on writing

The meat of the proof is in a lemma that establishes a weak
bisimulation between \ineffCEKD{} and \effCEK{C}.

>>>>

The main work of proof is in a lemma that establishes a weak
bisimulation between \ineffCEKD{} and \effCEK{C}.  The bisimulation
goes more smoothly if we require two more properties of the cast
representation: that the casts form a monoid (the $id$ and $seq$
operators) and that the cast constructor is equivalent to the identity
operator when applied to an identical source and target type.
